Dynein project log

### 2016-11-18 thesis_stuff/thesis_stuff.tex
add a citation to thesis_stuff
use bibtex for a couple of examples
Add program scaling information to thesis_stuff.tex. We can generate a single step in 6.5 hours at dt=10^-11s!

>>>>

\subsection{Program Scaling}
Program runtimes, as of commit 62c4d:

\begin{verbatim}
elliotc12@bennet:~/dynein_walk$ grep "dt" default_parameters.h 
double dt = 1e-11;
elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-5
Running for 1e-05 s

real	0m5.001s
user	0m4.972s
sys	0m0.000s
elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-5
Running for 1e-05 s

real	0m7.121s
user	0m7.072s
sys	0m0.000s
elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-4
Running for 0.0001 s

real	0m26.666s
user	0m26.608s
sys	0m0.000s
elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-4
Running for 0.0001 s

real	0m29.479s
user	0m29.428s
sys	0m0.000s
elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-3
Running for 0.001 s

real	4m47.224s
user	4m46.832s
sys	0m0.000s
elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-3
Running for 0.001 s

real	4m56.207s
user	4m55.776s
sys	0m0.000s
elliotc12@bennet:~/dynein_walk$ time ./generate_stepping_data --runtime=1e-2
Running for 0.01 s

real	61m44.302s
user	61m35.264s
sys	0m0.120s
\end{verbatim}

The average time per iteration is ~3.9 microseconds, or 3.9e5 real seconds per simulated second at $dt=10^{-11}s$. Thus we can generate one 60-millisecond step in 23,400 seconds, or 6.5 hours. A thousand-step simulation would thus take, very roughly, 8 months.\\
